One more attempt on ArXe

### 2015-03-18 theory.tex
add channel pic

In all autoionization processes considered, a second electron
is emitted with the kinetic energy $E_{sec}$. If $E_{sec}<0$, then
the final state energy is higher than the initial state energy and the        
process is energetically not accessible. Hence, the corresponding channel     
is closed.

>>>>

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.7]{pics/channel_open_ICD.pdf}
 \caption{Initial and final state energies for ArXe pairs at different
          distances using the experimental ionization potentials as given
          in Table \ref{}. For distances larger than the channel opening
          distance the ICD channel is open.}
 \label{figure:channel_open_ICD}
\end{figure}

In all autoionization processes considered, a second electron
is emitted with the kinetic energy $E_{sec}$. If $E_{sec}<0$, then
the final state energy is higher than the initial state energy and the        
process is energetically not accessible. Hence, the corresponding channel     
is closed as shown in Figure \ref{figure:channel_open_ICD}.
